---
title: "Exercises-intro-git-summer-2020"
output: html_document
---

#Introduction to Workflow

See git-cheat-sheet.pdf file in the repository.

#Exercise 1 (Group)

Together as a group, we'll go through a complete cycle of the github workflow to contribute to code. In this set, we'll create a new repository using a template, clone the repository, and make code contributions to it. (As we go through together, Ben will be "Person 1" and Jesse will be "Person 2".)

```{r make a function to multiply by three}
mult5 <- function(x){
  return()
}

mult3(2) #Should return the value 10
```

#Setup (Breakout Room)
1, Person 1's repository will be used for the remaining exercises. 
2. Person 1 adds person 2 as an admin in their repository.
3. Person 2 clones person 1's github repository, and using the git URL creates a new RStudio Cloud instance.
4. Person 2 adds in their github credentials (sorry, not saved across instances!)

#Exercise 2 (Breakout Room - person 1)

Complete the function so that it adds the value five to a given input, x.
Person 1 should make the change in code, and person 2 should manage the pull request.

##Steps

*Person 1:*

1. Create new branch (top right corner, git tab, branch icon). Name the branch "Exercise-2". The defaults settings work.

2. Complete the function below. Save your work.

3. Stage - click box beside file name in the git window.

4. Commit - Write a commit message that completes the statement "With this commit I"....

5. Push - click the "up" arrow in the git tab to send your changes to the remote repository. You'll have to enter your github credentials. 

6. In the GitHub repository, make a pull request for the change.

*Person 2:*
7. Person 2 manages the pull request, merges and closes it. (In actuality/real world, we'd test the code before closing the pull request.)

*Both People*
8. Pull the master branch back down to your local repository.

```{r person one codes}
add5 <- function(x){
  return()
}

add5(10) # Should return the value 10
```

#Exercise 2 (Breakout Room - person 2)

Follow the above steps, but now person 2 do steps 1 - 6 for the function below, and person 1 do step 7.  Person 2 should begin by first clicking Pull (down arrow) to update your local repository with the remote changes.

Complete function so that it divides a given input, x, by the value 2.
Person 2 should make the change in code, and person 1 should manage the pull request.
```{r person two codes}

div2 <- function(x){
  return()
}

div2(20) # Should return the value 10
```

#Exercise 3 (Group)

Now, we will go through the same steps again, but using the command line. Charreau will be "person 1" and "Ben will be person 2". 

Complete the function so that it returns an input, x, to the power of 2. 

```{r make function to square a value}
power2 <- function(x){
  return()
}

power2(5) #Should return 25
```

#Exercise 4 (Breakout Room - part 1)

Complete the function so that it returns the square root of an input value, x.
Person 1 should make the change in code, and person 2 should manage the pull request.

*Person 1:*

1. Create a new branch named "Exercise-4" using the following commands:
git checkout -b exercise-4 
git push -u origin exercise-4

Check to see what branch you're on using: git branch
Check the status of your git repository using: git status

2. Complete the function below. Save your work.

3. Stage changes using the following command:
git add Exercise-intro-git-summer-2020.Rmd

4. Commit - Write a commit message (replace 'commit_msg' in the command below) that completes the statement "With this commit I"... and execute the following command:
git commit -m "commit_msg"

5. Push - Send your changes to the remote repository using the following command.  You'll have to enter your github credentials:
git push origin exercise-4

6. In the GitHub repository, make a pull request for the change.

*Person 2:*
7. Person 2 manages the pull request, merges and closes it. (In actuality/real world, we'd test the code before closing the pull request.)

*Both People*
8. Pull the master branch back down to your local repository.

```{r make function for square root of value}
square_root <- function(x){
  return()
}

square_root(144) #Should return the 12
```

#Exercise 4 (Breakout Room - part 2)
Complete the function so that it returns the sum of a given input vector, x.
Person 2 should make the change in code, and person 1 should manage the pull request.

Follow the above steps, but now person 2 do steps 1 - 6 for the function below, and person 1 do step 7.  Person 2 should begin by first running the command:
git pull origin master
to update your local repository with the remote changes.
```{r make function for sum of vector}
sum_all <- function(x){
  return()
}

sum_all(x = c(1,2,3)) #Should return 6
```